Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
modify g0 main proof, minor other style edits

The following lemma provides an inductive method to extend O'Dorney's result on $\mathbf{P}^1$ to divisors $D=\sum_i \frac{\alpha_i}{\beta_i}P_i$ consisting of arbitrarily many points satisfying $H^0(X,\lfloor D\rfloor)>0$, showing that they are generated in degrees at most $e=\max(\beta_i)$ with relations generated in degrees at most $2e$.  Furthermore, given some constraints on $H^0(X, \lfloor dD\rfloor)$ for various values of $d$, we can apply the same Riemann-Roch arguments from $\mathbf{P}^1$ in arbitrary genus, allowing a similar inductive result in arbitrary genus $e=\max(\beta_i)$.  To do this, we extend an inductive result by Voight and Zurich-Brown on stacky canonical rings to arbitrary $\mathbf{Q}$-divisors. \todo{cite theorem 8.3.1}

@@

For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$. In both cases we induce a relation, with initial term described in the Lemma's statement. Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations $'s$ of the canonical divisor for
all cases where $g = 0, \delta = 0$ as defined in Definition
~\ref{defn:sat}. The saturation can be computed via the application
of Riemann-Roch on degrees up to $'s$. Exceptional cases are listed
first and generic cases follow.

@@

\begin{proof}
If $\sx$ has no stacky points, then we have the classical
case which is done in Voight and Zureick-Brown ~\cite[Section 4.2]
{vzb:stacky}. \todo{This confused me because while they do technically prove this, they only prove it for the canonical divisor, not the log canonical divisor. It would be clearer to write that in this case, we can assume $L = n \cdot \infty$ with $n \in \BZ$, which is covered in 4.2, with $L$ replaced by $K$.}

Now let us consider the case when $\delta \geq 2$. In any such case,
$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
the Lemma inductively on the classical case with no stacky points
to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-three-induction-g-0} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here \todo{Write this out more precisely, it should be something like $'sat(Eff(\sigma)) = 3$}), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.

So if $r > 5$, then $\sigma$ ``lies above'' \todo{Aaron: what does this mean} the case $(\sigma', J)$
where $\sigma'$ has $r$ many stacky points all of order $3$
and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
all of the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
If $r \leq 5$, then $\sigma$ ``lies above'' one of the base cases
of Lemma ~\ref{lem:g_0_admissible_cases}, all of which satisfy
the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.

>>>>

The following lemma provides an inductive method to extend
O'Dorney's result on $\BP^1$ to divisors $D = \sum_i \frac{\alpha_i
}{\beta_i} P_i$ consisting of arbitrarily many points satisfying $H^
0(X, \lfloor D \rfloor) > 0$, showing that they are generated in
degrees at most $e = \max(\beta_i)$ with relations generated in
degrees at most $2e$.  Furthermore, given some constraints on $H^0(
X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
same Riemann-Roch arguments from $\BP^1$ in arbitrary genus,
allowing a similar inductive result in arbitrary genus $e = \max(
\beta_i)$. To do this, we extend an inductive result by Voight and
Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
divisors. \todo{cite theorem 8.3.1}

@@

For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$. In both cases we induce a relation, with initial term described in the lemma's statement. Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations $s$ of the canonical divisor for
all cases where $g = 0, \delta = 0$ as defined in Definition
~\ref{defn:sat}. The saturation can be computed via the application
of Riemann-Roch on degrees up to $s$. Exceptional cases are listed
first and generic cases follow.

@@

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ$. This is the classical
case which is done, with $L$ replaced by $K$, by Voight and
Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.

Now let us consider the case when $\delta \geq 2$. In any such case,
$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
the lemma inductively on the classical case with no stacky points
to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-three-induction-g-0} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
{ssec:g_0_saturation} that $sat(Eff(\sigma_{11})) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, these cases satisfy all of the
conditions of Theorem ~\ref{thm:ram_order_ind}.

So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
where $\sigma'$ has $r$ many stacky points all of order $3$
and $J = \{1, \ldots, r\}$ in the sense that for all $i
\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
If $r \leq 5$, then $\sigma$ similarly ``lies above'' one of the
base cases of Lemma ~\ref{lem:g_0_admissible_cases}, all of which
satisfy the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.
